%IMPORTANT:  Change the page number on the first line below from 42 to whatever the first page number% should be in your bibliography.
\setcounter{page}{60}
\renewcommand{\thepage}{\arabic{page}}
\pagestyle{plain}



\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\MR}{\relax\ifhmode\unskip\space\fi MR }
% \MRhref is called by the amsart/book/proc definition of \MR.
\providecommand{\MRhref}[2]{%
  \href{http://www.ams.org/mathscinet-getitem?mr=#1}{#2}
}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{999}

\bibitem{Abou08}
Ahmed Abouelaz and Abdallah Ihsane, \emph{Diophantine {{Integral Geometry}}}, Mediterranean Journal of Mathematics \textbf{5} (2008), no.~1, 77--99.

\bibitem{Abou09}
Ahmed Abouelaz, Enrico~Casadio Tarabusi, and Abdallah Ihsane, \emph{Integral {{Geometry}} on {{Discrete Grassmannians}} in {{Zn}}}, Mediterranean Journal of Mathematics \textbf{6} (2009), no.~3, 303--316.

\bibitem{Bake81}
George~A. Baker and P.~R. {Graves-Morris}, \emph{Pad\'e approximants}, Encyclopedia of Mathematics and Its Applications ; {{Section}}, {{Mathematics}} of Physics, no. v. 13-14, Addison-Wesley, Advanced Book Program, Reading, Mass, 1981.

\bibitem{B2021}
Stoyu~T. Barov, \emph{Smooth convex bodies in {$\mathbb R^n$} with dense union of facets}, Topology Proc. \textbf{58} (2021), 71--83. \MR{4115754}

\bibitem{BCCT05}
Jonathan Bennett, Anthony Carbery, Michael Christ, and Terence Tao, \emph{Finite bounds for h{\"o}lder--brascamp--lieb multilinear inequalities}, Mathematical Research Letters \textbf{12} (2005), no.~4, 443--457.

\bibitem{Beyl87}
G.~Beylkin, \emph{Discrete radon transform}, IEEE Transactions on Acoustics, Speech, and Signal Processing \textbf{35} (1987), no.~2, 162--172.

\bibitem{bogachev_gaussian_1998}
V.~I. Bogachev, \emph{Gaussian measures}, Mathematical surveys and monographs, no. v. 62, American Mathematical Society, Providence, R.I, 1998 (eng).

\bibitem{BL76}
H.~J. Brascamp and E.~H. Lieb, \emph{Best constants in young's inequality, its converse and its generalization to more than three functions}, Advances in Mathematics \textbf{20} (1976), no.~2, 151--172.

\bibitem{Cuyt05}
Annie Cuyt, \emph{Multidimensional integral inversion, with applications in shape reconstruction}, SIAM Journal on Scientific Computing \textbf{27} (2005), no.~3.

\bibitem{Cuyt84}
\bysame, \emph{{P}ad\`e approximants for operators: Theory and applications'}, Springer-Verlag, 84.

\bibitem{DuXu01}
Charles~F. Dunkl and Yuan Xu, \emph{Orthogonal polynomials of several variables}, Encyclopedia of {{Mathematics}} and Its {{Applications}}, vol.~81, Cambridge University Press, Cambridge, 2001. \MR{1827871}

\bibitem{ELR1970}
Larman D.~G. Ewald, G. and C.~A. Rogers, \emph{The directions of the line segments and of the r ‐dimensional balls on the boundary of a convex body in euclidean space}, Mathematika \textbf{17 no. 1} (1970), 1–20.

\bibitem{Helg65}
S.~Helgason, \emph{The {R}adon transform}, Birkh\"auser, 1965.

\bibitem{Seng12}
Irina Holmes and Ambar~N. Sengupta, \emph{A {G}aussian {R}adon transform for {B}anach spaces}, J. Funct. Anal. \textbf{263} (2012), no.~11, 3689--3706. \MR{2984081}

\bibitem{Seng14}
\bysame, \emph{The {G}aussian {R}adon transform in classical {W}iener space}, Commun. Stoch. Anal. \textbf{8} (2014), no.~2, 247--268. \MR{3269847}

\bibitem{LPP2016}
G.~Livshyts, G.~Paouris, and P.~Pivovarov, \emph{On sharp bounds for marginal densities of product measures}, Israel Journal of Mathematics \textbf{216} (2016), 877--889.

\bibitem{Miha04}
Vochita Mihai, \emph{The {{Radon-Gauss}} transform}, Doctor of {{Philosophy}}, Louisiana State University and Agricultural and Mechanical College, May 2004.

\bibitem{Pete82}
L.~C. Petersen, \emph{On the relation between the multidimensional moment problem and the one-dimensional moment problem}, Math. Scand. \textbf{51} (1982), no.~2, 361--366. \MR{690537}

\bibitem{Rado17}
Johann Radon, \emph{{\"U}ber die {B}estimmung von {F}unktionen durch ihre {I}ntegralwerte l\"angs gewissermannigfaltigkeiten},  (1917).

\bibitem{Rado86}
\bysame, \emph{On the determination of functions from their integral values along certain manifolds},  (1986).

\bibitem{Rote97}
G\"unter Rote, \emph{Finding a shortest vector in a two-dimensional lattice modulo {$m$}}, Theoret. Comput. Sci. \textbf{172} (1997), no.~1-2, 303--308. \MR{1432870}

\bibitem{S2014}
Rolf Schneider, \emph{Convex bodies: the brunn-minkowski theory, second expanded edition}, Cambridge University Press, 2014.

\bibitem{Stro71}
A.~H. Stroud, \emph{Approximate calculation of multiple integrals}, Prentice-Hall, 1971.

\bibitem{Sval03}
Imants Svalbe and Andrew Kingston, \emph{Farey sequences and discrete {R}adon transform projection angles}, 9th {I}nternational {W}orkshop on {C}ombinatorial {I}mage {A}nalysis, Electron. Notes Discrete Math., vol.~12, Elsevier Sci. B. V., Amsterdam, 2003, p.~12. \MR{2155842}

\bibitem{Than93}
Sundaram Thangavelu, \emph{Lectures on {{Hermite}} and {{Laguerre}} expansions}, Mathematical Notes, no.~42, Princeton University Press, Princeton, N.J, 1993.

\bibitem{Zalc82}
Lawrence Zalcman, \emph{Uniqueness and nonuniqueness for the {R}adon transform}, Bull. London Math. Soc. \textbf{14} (1982), no.~3, 241--245. \MR{656606}

\end{thebibliography}
