% \chapter{Long Title}{Short Title}
% The Long Title will appear on the first page of the chapter.
% The Short Title will appear in the table of contents.
% If the Long Title isn't all that long, you can just call
% \chapter{Long Title}{} and the same title will appear in
% both places.


\chapter{Shape reconstruction from moments}{}

In this chapter we describe a method for shape reconstruction from moments and propose an extension of the method to unbounded regions. In the first section we summarize the method for bounded sets. This is the work of Cuyt et al.~\cite{Cuyt05} which we extend in the following sections to unbounded shapes and positive functions of at most polynomial growth. The methods all each have the basic structure:
\begin{enumerate}
  \item From moments of $f$ compute Pad\'e approximants to its Stieltjes transform.
  \item Choosing a set of nodes on which to approximate $f$, construct an appropriate cubature formula to the Stieltjes transform.
  \item Solve — or approximate a solution to — the linear system given by equating the Pad\'e approximants and cubature formula. 
\end{enumerate}

\section{Reconstruction of bounded shapes}

% Suppose $A \subseteq \RR^n$ is a bounded measurable set. Then it has finite multivariate moments
% \[
%   c_\alpha = \int_{A} x^{\alpha} ~dx.
% \]
% For any $\omega \in S^{n-1}$ the RT is well defined,
% \[
%   R_A(\omega, p) = \int_A 1_{\inner{x, \omega} = p} dx
% \]
% and measurable as a function of $p \in \RR$ \cn. The integral of $R_A(\omega, p)$ over $p \in \RR$ is the measure of $A$ by Fubini's theorem. By \cn\ the projection moments
% \[
%   c_k(\omega) = \int_A 1_{\inner{x, \omega} = p} p^k dp
% \]
% are finite and determinate. The Stieltjes transform
% \[
%   g_{\omega}(z) = \int_{-\infty}^\infty \frac{R_A(\omega, p)}{1 + pz} ~dp = \sum_{k = 0}^\infty c_k(\omega) (-z)^k
% \]
% is analytic at $z = 0$ and has uniformly convergent off-diagonal Pad\'e approximants $R_M(z)$. The rate of convergence in this case can be controlled further by \cn. On the other hand $g_\omega(z)$ can be approximated as an integral by a cubature formula
Suppose $A \subseteq \RR^n$ is a bounded measurable set with indicator function $f$. Then it has finite multivariate moments
\[
  c_\alpha = \int_{A} x^{\alpha} ~dx.
\]
The projection moments for any $\omega \in S^{n-1}$, given by
\[
  c_k(\omega) = \sum_{|\alpha| = k} \binom{k}{\alpha} c_\alpha \omega^\alpha
\]
are coefficients to the Stieltjes series
\[
  \sum_{k = 0}^\infty c_k(\omega) (-z)^k,
\]
which is converges in a neighborhood of $z = 0$ to the Stieltjes transform
\[
  g_{\omega}(z) 
  = \int_{-\infty}^\infty \frac{R_A(\omega, p)}{1 + pz} ~dp 
  = \int_{A} \frac1{1 + z\inner{x, \omega}}~dx. 
\]
Note that since $A$ is bounded, say by $\norm{x} \leq r$ for all $x \in A$, then $RT_A(\omega, p)$ vanishes for $|p| > r$. Singularities in the integrand can only occur when $z = -1/p$ so we conclude $g_\omega(z)$ is well defined for $|z| < 1/r$. 

Recall that since $A$ is bounded, it has determinate multivariate moments and projection moments. By corollary~\ref{cr:determinacypade}, $g_{\omega}(z)$ is the uniform limit of the off-diagonal Pad\'e approximants $R_M(z)$ to the Stieltjes series. The rate of convergence in this case is known, and can be found in~\cite{Bake81}.

We consider $g_\omega(z)$ as the restriction of the multivariate Stieltjes transform
\[
  g(y) = \int_{A} \frac{1}{1 + \inner{x, y}} dx, \qquad y \in \RR^n
\]
to a the linear span of $\omega \in S^{n-1}$. That is, for $z \in \RR$,
\[
  g(z\omega) = \int_{A} \frac{1}{1 + z\inner{x, \omega}} dx = g_\omega(z).
\]
Here $g(z\omega)$ is well defined for $|z| < 1/r$ so that the multivariate transform is well defined for $\norm{y} < 1/r$. For any $y \in \RR^n$, we can compute projection moments with $\omega = y/\norm{y}$, from which we can approximate $g(y) = g_\omega(\norm{y})$ by way of the Pad\'e approximants described above. Let us denote this approximation by $\tilde g(y)$. 

Now suppose $g(y)$ can be simultaneously approximated by a cubature formula
\[
  \sum_{i = 0}^I w_i(y) f(x_i) \approx \int_{A} \frac1{1 + \inner{x, y}}~dx,
\]
where $f(x) = 1_A(x)$. Consider the linear system,
\[
  \sum_{i = 0}^I w_i(y_j) \tilde f_i = \tilde g(y_j), \qquad j = 0, \ldots, J
\]
where $y_0, \ldots, y_J \in \RR^n$ are a set of distinct sample points with $y_i < 1/r$ and $J > I$. At least heuristically, we expect a solution to this system in the form of the values to approximate the values of the characteristic function
\[
  \tilde f_i \approx f(x_i), \qquad i = 0, \ldots, I,
\]
at the cubature nodes $x_i$. Thus, if for example, we use a cubature formula with nodes $x_i$ on a finite integer lattice around $A$, we will have computed an approximate pixel image of $A$.

Our discussion thus far clearly avoided some technical details. The choice of cubature formula and well-posedness of the linear system are obvious concerns, which we touch on briefly in section \ref{sec:implementation}.

\section{Reconstruction of unbounded shapes}

Our proposed extension to the method above follows roughly the same trajectory, but applies to a much broader class of functions. We will start with the prime example of indicator functions of unbounded measurable sets, and discuss the generalization in the next section.

Let $A \subseteq \RR^n$ be a measurable set with indicator function $f$. Then $f$ necessarily has finite Gaussian moments,
\[
  c^\gamma_\alpha = \int_{\RR^n} f(x) x^\alpha \gamma_n(x) ~dx.
\]
The Gaussian projection moments for any $\omega \in S^{n-1}$ are given by
\[
  c^\gamma_k(\omega) = \sum_{|\alpha| = k} \binom{k}{\alpha} c^\gamma_\alpha \omega^\alpha.
\]
Now the Stieltjes series
\[
  \sum_{k = 0}^\infty c^\gamma_k(\omega) (-z)^k
\]
is generally formal. Likewise, the Stieltjes transform
\[
  g^\gamma_\omega(z) := \int_{-\infty}^\infty \frac{GR_A(\omega, p)}{1 + pz} \gamma(p)~dp = \int_A \frac{1}{1 + z\inner{x, \omega}} \gamma_n(x) ~dx
\]
may be undefined on the real line, but is analytic on the half planes $\im z \neq 0$. In this case the Stieltjes series is an asymptotic expansion to the Stieltjes transform in the sense of nontangential convergence,
\[
  g^\gamma_\omega(z) \simeq \sum_{k = 0}^\infty c^\gamma_k(\omega) (-z)^k.
\]
For more details on the Stieltjes series and transform in the case of Hamburger moments see section \ref{sec:stieltjes}. 

Now we note that $GR_A(\omega, p)$ is a bounded function, so that the Gaussian projection moments are determinate. Thus, as discussed in section \ref{sec:pade}, the $[M-1/M]$ Pad\'e approximants to the Stieltjes series converge locally uniformly on the half planes to the Stieltjes transform.

Once again, we view $g^\gamma_\omega(z)$ as a restriction of a multivariate Stieltjes transform. Following the lead of the previous method, we consider the function $g^\gamma : \CC^n \to \CC^n$ given by the integral representation
\[
  g^\gamma(y) = \int_{A} \frac{1}{1 + \inner{x, y}} \gamma_n(x) ~dx
\] 
whenever well defined. Here $\inner{\cdot, \cdot}$ is the standard inner product on $\CC^n$. We have seen that $g^\gamma(y)$ exists when $y = z\omega$ for $\omega \in S^{n-1}$ and $z \in \CC$ has nonzero imaginary part,
\[
  g^\gamma(z\omega) 
  = \int_{A} \frac{1}{1 + z\inner{x, y}} \gamma_n(x) ~dx
  = g^\gamma_\omega(z)
\]
(We assume the complex inner product is conjugate linear in the first variable and linear in the second for simplicity). 

Again, suppose $g^\gamma(y)$ can be simultaneously approximated by a cubature formula
\[
  \sum_{i = 0}^I w_i(y) f^\gamma(x_i) \approx \int_{A} \frac1{1 + \inner{x, y}} \gamma_n(x) ~dx,
\]
where $f^\gamma(x) = 1_A(x)\gamma_n(x)$. Consider the linear system,
\[
  \sum_{i = 0}^I w_i(y_j) \tilde {f}^\gamma_i = \tilde g^\gamma(y_j), \qquad j = 0, \ldots, J
\]
where $y_0, \ldots, y_J \in \CC^n$ are a set of distinct sample points and $J > I$. In this case we require our sample points to take the form $y = z\omega$ sufficient for the existence of $g^\gamma(y)$. At least heuristically, we expect a solution to this system in the form of the values to approximate the values
\[
  \tilde f^\gamma_i \approx f^\gamma(x_i), \qquad i = 0, \ldots, I,
\]
at the cubature nodes $x_i$. In order to approximate $A$ we simply remove the Gaussian weight,
\[
  \frac{\tilde f^\gamma_i}{\gamma_n(x_i)} 
  \approx \frac{f^\gamma(x_i)}{\gamma_n(x_i)}
  = 1_A(x_i).
\]

Here we may still use a finite lattice to produce a pixel image, but importantly neither the sample points $y_i$ nor the Pad\'e approximant $\tilde g^\gamma$ depend on the choice of cubature formula. In other words, with $\tilde g^\gamma(y_j)$ precomputed, image approximations to $A$ can — in theory — be constructed for arbitrary pixel grids. We suspect that careful choice of cubature formulas may lead to additional redundancy in computing the weights $w_i(y_j)$.

% \[
%   g_\omega(z) 
%   = \int_A \frac{1}{1 + z\inner{x, \omega}} w_n(x) ~dx 
% \]

% \[
%   g(y) = \int_A \frac{1}{1 + \inner{x, y}} w_n(x) ~dx,
% \]
% however we can not in general expect this transform to exist for any real $y$. In particular, for $z$ in the upper half plane $\im z > 0$ and $\omega \in S^{n-1}$ we have
% \[
%   g(z\omega) 
%   = \int_A \frac{1}{1 + z\inner{x, \omega}} w_n(x) ~dx 
%   = g_\omega(z).
% \]
% Thus for complex vectors of the form $y = z\omega$

% Take a non-negative Lebesgue measurable function $f(x)$ on $\RR^n$ with finite multivariate Gaussian moments
% \[
%   c^G_\alpha = \int_{\RR^n} f(x)e^{-\|x\|^2/2} x^\alpha dx
% \]
% We have seen that the multivariate Stieltjes transform of $f(x)w_n(x)$, 
% \[
%   g(z) = \int_{\RR^n} \frac{f(x)e^{-\|x\|^2/2}}{1 + \langle x, \omega \rangle z} dx,
% \]
% is equal to the Hamburger transform of $GR_f(\omega, p)$, whose moments in turn are easily computed from the moments of $f$, for fixed $\omega$. Thus for $z$ in the one dimensional subspace spanned by $\omega$, $g(z)$ can be approximated well by Pad\'e approximants, under the integrability condition $GR_f(\omega, p) \in L^2(\RR, e^{-p^2}~dp)$. On the other hand as an integral on $\RR^n$, we can also approximate $g(z)$ by cubature formula,
% \[
%   \int_{\RR^n} \frac{f(x)e^{-\|x\|^2/2}}{1 + \langle x, \omega \rangle z} dx 
%   \approx \sum_{\ell = L} \frac{e^{-\|x_\ell\|^2/2}}{1 + \langle x_\ell, \omega \rangle z} w_\ell f(x_\ell)
%   =: \sum_{\ell = L} C_\ell(z) f(x_\ell).
% \]
% By equating these parallel approximations, 
% \[
%     \sum_{\ell = L} C_\ell(z) f(x_\ell) \approx R_M(z),
% \]
% with a sufficient quantity of sample points $z_j$ we have arrived at a linear system
% \[
%   \sum_{\ell = L} C_\ell(z_j) f(x_\ell) = R_M(z_j), 
%   \qquad j = 1, 2, \ldots, J
% \]
% from which we should be able to recover the value of $f$ on our cubature nodes $x_\ell$.



% We have seen that the Hamburger transform of the GRT of $f$,
% \[
%     g(z) = \int_{-\infty}^\infty \frac{GR_f(\omega, p) e^{-p^2/2}}{1 + pz}dp
% \]
% can be approximated to an arbitrary degree by offdiagonal Pad\'e approximants, $R_M(z)$ near zero. On the other hand as an integral over $p$

\section{Reconstruction of functions in weighted $L^2$ space}

As discussed in section \ref{sec:GRTdeterminacy}, the Gaussian moments of a function in the weighted space $L^2(\gamma_n)$ are determinate. Thus the method for unbounded shape reconstruction evidently applies just as well to all measurable functions $f: \RR^n \to [0, \infty)$ which satisfy
\[
  \int_{\RR^n} f(x)^2 \gamma_n(x) ~dx < \infty.
\]
We will not repeat the construction, but in short, the Gaussian Moments
\[
  c^\gamma_\alpha = \int_{\RR^n} f(x) x^\alpha \gamma_n(x) ~dx \qquad \alpha \in \NN_0^n
\]
can be used to approximate a multivariate Stieltjes transform
\[
  g(y) = \int_{\RR^n} \frac{f(x)}{1 + \inner{x, y}} \gamma_n(x) ~dx
\]
where $y \in \CC^n$ is required to take a specific form. Simultaneously approximating $g(y)$ by a cubature formula, we forma a linear system for which approximate values of $f$ on the cubature nodes is a solution. 

\section{Implementation and practical limitations} \label{sec:implementation}

Here we will briefly discuss some of the computational aspects in implementation of the shape reconstruction methods. The following discussion is based on a series of examples tested in Mathematica, and is not intended to be rigorous.

To the best of our knowledge, no rigorous analysis of the presented methods from a numerical or computational perspective exist. Nor are we qualified to undertake such an analysis ourselves. Of the most obvious concerns are the accuracy of the cubature approximation, the solvability of the high dimensional linear system, and stability with respect to errors in moments.

While any sufficiently accurate cubature formula should work, those with nodes on a uniform cubic lattice – trapazoid and Simpson's formulas, e.g. – have the benefit of producing an approximation easily visualized as a grayscale pixel image. Product formulas formed from compound Gaussian quadrature rules should also be considered. Indeed the examples in \cite{Cuyt05} are computed using a compound two-point Gauss-Legendre formula. Such cubature formulas have nodes on a "nearly" uniform cubic grid, leading to some distortion when viewed as an image, however the distortion scales down as image resolution increases. 

For the proposed extensions to the method, we suggest a product Gauss-Hermite formula, whose nodes are given by the cartesian product of the zeros of a Hermite polynomial. This is a natural choice for numerical integration with a Gaussian weight. Importantly, we expect a good degree of accuracy due to the density of polynomials in $L^2(\gamma_n)$. Furthermore the zeros of Hermite polynomials have roughly uniform spacing, and it is common practice to ``prune'' the nodes furthest from the origin where spacing is most distorted. The nodes and weights for Gauss-Hermite cubature can be computed efficiently even for high degrees. For increasing degree, we get smaller spacing over a larger neighborhood. 

In experiments we have found the most computationally intensive portion of the method to be the formation and solving of the linear system. Unsurprisingly, for even the mildest examples, this system tends to be higly dimensional and generally ill-determined. The authors of \cite{Cuyt05} suggest using a truncated singular value decomposition, discarding singular values below a threshold. We have had reasonable success via Mathematica's \Verb|PsuedoInverse| method. We should also note that the introduction of non-real terms in the proposed methods presents some additional complications. In particular, approximate solutions tend to be complex valued.

Finally, we should discuss the elephant in the room. The discrete reconstructions formed by our methods are necessarily finite, which is at odds to their utility as approximations to unbounded objects. One might propose instead applying the method for bounded shape reconstruction where we restrict unbounded objects to some bounded region. We argue that even in constructing a finite approximation, there is some benefit to working with global information. Assuming one has access to the Gaussian moments, it is convenient that our method does not impose an arbitrary ristriction on the scale of the object. Consider a situation where we would like to construct a series of improving approximations to an unbounded object. Since the approximate sample values $\tilde g^\gamma (y_j)$ can be precomputed (and further sample points $y_j$ can be added at little cost), we are able to increase both the overall size of the approximation as well as the granularity of node spacing without much adjustment. 
% In particular when using Gauss-Hermite cubature, 

There is much more to be said on the practical limitations of these methods, but as we have hopefully shown, their theoretical foundation is solid and there is good reason to expect them to work in practice. Further investigation into the questions of numerical stability and computational efficiency is needed.



% We have spent some time implementing our proposed extension to the shape reconstruction method, mostly in the Wolfram Mathematica language. But of course in this process questions arose, both theoretical and pragmatic. 
% % We are limited in our knowledge of numerical and computational analysis, and welcome criticism.

% While the authors describe forming multivariate ``homogeneous'' Pade approximants — perhaps first proposed by Cuyt herself in~\cite{Cuyt84} — we opt to bypass this step using univariate approximants instead. Indeed, the only benefit to Cuyt's approximants explicitly cited by the authors, as compared to other multivariate generalizations of the Pade approximants, is that they are ``the only satisfying the following powerful slice theorem''~\cite{Cuyt05}. This slice theorem simply states that the homogeneous approximants when restricted to one dimensional subspaces, are equivalent to univariate Pade approximants. Since we only need a finite number of sample points it seems reasonable to compute a series of univariate approximants at various projection angles.

% The decision to drop the homogenous approximants has the following potential consequences: On the one hand, the univariate approximants are simpler to compute, with methods built in to many CASs. On the other, while the authors select sample points from a cubic lattice, it would be inefficient (though potentially less so with careful selection of projection angles via, say, Farey sequences) to do so with one dimensional subspaces. Instead we take a collection of equidistant projection angles forming a radial grid of sample points. This seems acceptable, as it is unclear if there is any benefit to the sample points having a particular geometric structure. We should also agknowledge the potential that forming a single homogeneous appoximant is more computationally efficient than many univariate approximants. This requires further investigation, but we note that (anecdotally) in computational tests the formation of approximants is not very intensive compared to the subsequent solving of the high dimensional linear system. Some thought was given to the possibility that sampling from a cubic lattice provides some structure which makes the system easier to solve, but so far we have no hard evidence of this.

% A couple of notes on computational details: First we should be explicit about the line of computation. At the outset, the given information is a certain multivariate moment sequence (up to a finite order with some accuracy assumption) which we assume belongs to a region within some fixed bounding box. In evaluating the computational viability of the method we take note of which steps depend on the moments, and which can be precomputed. In order to form univariate approximants we first compute projection moments. While these of course depend on the moment sequence, the multinomial formula used for this computation only depends on the projection angle. Thus with a preditermined set of projection angles this is partially precomputed. Since the cubature formula itself only depends on the choice of quadrature nodes and sample points, it can be precomputed and applied to any moment sequence. The choice of quadrature formula is somewhat arbitrary. Lacking expertise in the area of numerical integration, we follow the authors, opting for the four-point Gauss-Legendre product formula. This formula takes nodes from a nearly cubic lattice, which is implicitly quantized when forming the pixel image. We have not evaluated the error introduced by this quantization but expect it to be minimal and to approach zero with higher pixel resolution.

% We don't expect the linear system to have an exact solution, let alone one that whose computation is tractable for high resolutions. We may try Mathematica's LeastSquares method, but Cuyt et al.\ specifically mention using a truncated singular value decomposition.

% For my own benefit, let's review singular value decompositions. An $i \times j$ matrix $A$ of rank $r$ can be written as 
% \[
%   A=U\Sigma V^\top,
% \]
% where $\Sigma$ is the diagonal matrix of singular values $\sigma_1, \sigma_2, \ldots, \sigma_r$, and $U$ and $V$ are unitary matrices. The truncated singular value decomposition gives us a reduced rank approximation to $A$ by replacing all but the largest (first) $k$ singular values in $\Sigma$ with zeros,
% \[
%   \tilde{\Sigma} = \text{diag}(\sigma_1, \sigma_2, \ldots, \sigma_k, 0, \ldots, 0)
% \] 
% The truncated SVD matrix $\tilde{A} = U \tilde{\Sigma} V^\top$ is optimal in the sense that it is the closest rank-$k$ matrix to $A$ in the Frobenius norm.

% The SVD and truncated SVD are used to solve the linear least squares problem as follows: From $U\Sigma V^\top f = p$ we get $f=V \Sigma^{-1} U^\top p$, and similarly $f = \tilde{V} \tilde{\Sigma}^{-1} U^\top p$. Note that the psuedoinverse $\tilde\Sigma^{-1}$ is a diagonal matrix made up of the reciprocal singular values.

% Mathematica offers a few built in functions for this. LeastSquares packages a number of methods to solve a linear least squares based on the sparsity of the System (our system is dense). SingularValueDecomposition can be restricted to a certain number of singular values. PsuedoInverse can specify a ``tolerance'' zeroing out singular values less than some proportion of  the maximum singular value. While LeastSquares is the simplest option, it does not seem to support truncated solutions. Between SingularValueDecomposition and PsuedoInverse, both can handle truncated problems, but the latter seems — at least superficially — better suited for out application.

% On Gaussian shape reconstruction. There remain some minor practical concerns about, for example, the choice of quadrature formula and sample points. An obvious choice would be to continue with the Gauss-Legendre product formula, now applied on a Gaussian-weighted $f$. Some consideration should be taken as to the viability of other Gaussian quadrature formulas defined particularly for the Gaussian measure. 

% Now, a fundamental limitation with the proposed method which we have neglected to mention is the practical one: As a computational method we are necessarily restricted to the finite — finite moments, finite order approximations, and most problematic, bounded domains. In what application would one even be interested in unbounded shape reconstruction, while also having access of Gaussian moments? It would be reasonable to question the use of a computational method in an unbounded context. As with any finite approximation, the unboundedness should be thought of as an idealized limit; perhaps an unbounded approximation is a limit of bounded approximations. But then, the original method applies just as well if all we wanted was a sequence of reconstructions expanding in range. We can only speculate at this point that perhaps this method, being tailored specifically for unbounded reconstruction, could hold some practical advantages over its predecessor; or be satisfied with impracticality.


% \section{An example}

% \[
%     w(x) = w_1(x) = \frac1{\sqrt{2\pi}}e^{-\frac{x^2}2}
% \]
% \[
%     w_2(x, y) = \frac1{2\pi}e^{-\frac{x^2 + y^2}2}
% \]

% \[
%     f : \RR^2 \rightarrow \RR
% \]
% \begin{align*}
%   GR_f(\theta, p) 
%   &= \int_{-\infty}^\infty f(x(t), y(t)) w(t)~dt \\
%   &= \int_{-\infty}^\infty f(t \sin\theta + p \cos\theta, -t \cos\theta + p \sin\theta) w(t)~dt
% \end{align*}

% Let $f_{i,j} = x^i y^j$ for $i, j \in \NN_0$. Define $G_{i,j}(\theta, p) = GR_{f_{i,j}}(\theta, p)$
% \[
%     G_{i,j}(\theta, p)
%     = \frac1{\sqrt{2\pi}}\int_{-\infty}^\infty {(t \sin\theta + p \cos\theta)}^i {(-t \cos\theta + p \sin\theta)}^j e^{-\frac{t^2}2}~dt
% \]
% In particular 
% \begin{align*}
%     G_{0,0}(\theta, p) 
%     &= 1 \\
%     G_{1,0}(\theta, p) 
%     &= \frac1{\sqrt{2\pi}}\int_{-\infty}^\infty (t \sin\theta + p \cos\theta) e^{-\frac{t^2}2}~dt
% \end{align*}

% Let $H_\alpha(x) = H_{\alpha_1}(x_1)H_{\alpha_2}(x_2) \cdots H_{\alpha_n}(x_n)$ for $\alpha \in \NN_0^n$ and when $n=2$,
% \[
%   H_{i,j}(x,y) = H_i(x)H_j(y)
% \]
% Mathematica table: $\frac{GR_{H_{i,j}}(\theta,p)}{\cos^i\theta \sin^j\theta}$ for $i,j \leq 4$
% \[
%   \begin{array}{ccccc}
%     1 & p & p^2-1 & p^3-3 p & p^4-6 p^2+3 \\
%     p & p^2-1 & p^3-3 p & p^4-6 p^2+3 & p^5-10 p^3+15 p \\
%     p^2-1 & p^3-3 p & p^4-6 p^2+3 & p^5-10 p^3+15 p & p^6-15 p^4+45 p^2-15 \\
%     p^3-3 p & p^4-6 p^2+3 & p^5-10 p^3+15 p & p^6-15 p^4+45 p^2-15 & p^7-21 p^5+105 p^3-105 p \\
%     p^4-6 p^2+3 & p^5-10 p^3+15 p & p^6-15 p^4+45 p^2-15 & p^7-21 p^5+105 p^3-105 p & p^8-28 p^6+210 p^4-420 p^2+105 \\
%   \end{array}
% \]

% \textbf{Conjecture:} Based on a Mathematica table (at least up to $i,j\leq4$) it seems that the following formula holds:
% \[
%   GR_{H_{i,j}}(\theta, p) = H_{i+j}(p) \cos^i \theta \sin^j \theta 
% \]
% We further expect 
% \[
%   GR_{H_\alpha}(\omega, p) = H_{|\alpha|}(p) \omega^\alpha
% \]
% for $\alpha \in \NN_0^n$.

% Bogachev (for example): $(H_\alpha)_{\alpha \in \NN_0^n}$ is an orthogonal basis in $L^2(\gamma_n)$

% Mathematica table: $GR_f(a, p)$ for $f(x,y) = x^i y^i$
% \[
% \begin{array}{cccc}
%   1 & p \sin (a) & p^2 \sin ^2(a)+\cos ^2(a) & p \sin (a) \left(p^2 \sin ^2(a)+3 \cos ^2(a)\right) \\
%   p \cos (a) & \left(p^2-1\right) \sin (a) \cos (a) & p \cos (a) \left(\left(p^2-2\right) \sin ^2(a)+\cos ^2(a)\right) & \sin (a) \cos (a) \left(p^2 \left(p^2-3\right) \sin ^2(a)+3 \left(p^2-1\right) \cos ^2(a)\right) \\
%   p^2 \cos ^2(a)+\sin ^2(a) & p \sin (a) \left(\left(p^2-2\right) \cos ^2(a)+\sin ^2(a)\right) & \frac{1}{8} \left(-\left(p^4-6 p^2+3\right) \cos (4 a)+p^4+2 p^2+3\right) & \frac{1}{8} p \sin (a) \left(8 \left(p^2-3\right) \cos (2 a)-\left(p^4-10 p^2+15\right) \cos (4 a)+p^4+6 p^2-9\right) \\
%   p \cos (a) \left(p^2 \cos ^2(a)+3 \sin ^2(a)\right) & \frac{1}{4} \sin (2 a) \left(\left(p^4-6 p^2+3\right) \cos (2 a)+p^4-3\right) & \frac{1}{8} p \cos (a) \left(-8 \left(p^2-3\right) \cos (2 a)-\left(p^4-10 p^2+15\right) \cos (4 a)+p^4+6 p^2-9\right) & \frac{1}{16} \sin (2 a) \left(-\left(p^6-15 p^4+45 p^2-15\right) \cos (4 a)+p^6+9 p^4-27 p^2-15\right) \\
%   \end{array}
% \]

% \[
%   f(x) =
%   \begin{cases}
%     1, & \langle x, \varphi \rangle \leq 1/2 \\
%     0, & \text{otherwise}
%   \end{cases}
% \]

% First compare the methods on bounded regions: Unit ball in $\RR^3$? Annulus in $\RR^2$? Some asymmetric or off-center examples?

% More importantly, present examples for unbounded regions: Strips and cones come to mind. One-sided strips maybe. 

% How do we ``image'' an unbounded region in the first place? Our method places pixels upon the nodes of a cubature formula which is usually a bounded cubic lattice. What are appropriate nodes for, and how can we best ``image'' a region which does not fit within a bounded rectangle? 

% Language is hard





