\chapter{Krawtchouk Polynomials and a Discrete GRT}{}
\label{chap:DGRT}

Here we discuss discrete Radon transforms (DRTs) with the goal of developing a suitable discrete analogue to the Gaussian Radon transform (DGRT). Building on the formulas from the previous chapter we propose a DGRT defined via the Krawtchouk polynomials, which are discrete analogues to the Hermite polynomials.

\section{Discrete Radon Transforms}

Many discrete analogues to the classical transform have been proposed. In~\cite{Beyl87}, Beylkin proposes a DRT over a finite 2-dimensional lattice with an efficient inversion procedure. Abouelaz et al.~\cite{Abou08}~\cite{Abou09} give a DRT over $d$-dimensional affine sublattices of $\ZZ^n$ as well as dual transforms, support and inversion theorems in analogue to the $d$-plane extended RT. 

We argue that Beylkin's framework does not lend itself to the GRT setting because it lacks a distinguished origin point. Abouelaz et al.'s transform is a promising starting point for a DGRT worth investigating further. A key difference we should note is that the closest point of an affine sublattice to the origin does not in general coincide with the closest point of the corresponding affine subspace to the origin.

For now, we a new DGRT following a somewhat roundabout path via the formulas of chapter 4.

\section{Krawtchouk polynomials}

The formula (\ref{eq:GRH}) gives us a path toward defining a discrete analogue to the Gaussian Radon transform. 
% We will begin by introducing the binomial density and corresponding Krawtchouk polynomials.
We will begin with the simple random walk as a motivating example. 

Consider flipping $N$ fair coins, and counting the number of heads. We can model each coin by independant identically distributed (i.i.d.) random variables $X_t$, $t = 1, \ldots, N$ taking the value $0$ or $1$ with equal probability. Then the total number of heads is given by
$
  S_N = \sum_{t = 1}^{N} X_t.
$
Since the number of ways to choose $x$ coins to land on heads is $\binom{N}{x}$, we have the probabilities
\[
  P\{S_N = x\} = \frac1{2^n}\binom{N}{x}.
\]
This defines the density of the standard binomial distribution.

\begin{definition}
  The \emph{binomial distribution}, modeling the number of heads in $N$ flips of a possibly biased coin, has the density
  \[
    B_{N, p}(x) = \binom{N}{x} p^x(1 - p)^{N - x}, \quad x = 0, \ldots, N
  \]
  where $p$ is the probability that the coin lands heads. In the case of a fair coin $p = 1/2$ and we simply write
  \[
    B_N(x) = \binom{N}{x}.
  \]
\end{definition}

Now imagine taking a walk on the integer lattice $\ZZ$ where a coin flip decides whether we step to the right or left. If $p$ is the probability of stepping to the right, then the stochastic process
\[
  W_N 
  % = \sum_{t = 1}^N -1 + 2X_t 
  = -N + 2B_{N, p},
\]
represents our position after $N$ coin flips, assuming we start at the origin $W_0 = 0$. We can think of this as a centered binomial distribution. We will stick to the symmetric case $p = \frac12$.

\begin{definition}
  The \emph{symmetric simple random walk} in one dimension is a stochastic proccess $\{W_N\}_{N = 0}^\infty$ defined by
  \[
    W_N = 2B_{N} - N = \sum_{t = 1}^N (2X_t - 1)
  \]
  where $2X_t - 1$ takes the values $\pm 1$ with equal probability.
\end{definition}

Some immediate properties can be deduced by i.i.d. random variables $2X_t - 1$. For instance, we have the mean
\[
  \mathrm{E}[W_N] = \sum_{t = 1}^N \mathrm{E}(2X_t - 1) = 0,
\]
and variance
\[
  \mathrm{Var}[W_N] = \sum_{t = 1}^N \mathrm{Var}[2X_t - 1] = \sum_{t = 1}^N 1 = N.
\]
Furthermore we can compute characteristic function
\[
  \mathrm{E}[e^{isW_N}] = \prod_{t = 1}^N \mathrm{E}[e^{is(2X_t - 1)}] = \left(\frac{e^{is} - e^{-is}}2\right)^N = \cos^N(s).
\]

We would like to understand assymptotic charactaristics of $W_N$ as $N \to \infty$, but we quickly run into a problem. 


\begin{proposition}
  The normalized binomial distribution $\tilde{W}_N = \frac1{\sqrt{N}}W_N$ converges in distribution to the standard Gaussian $\gamma$.
\end{proposition}

\begin{proof}
  Since $W_N$ is defined as a sum of i.i.d. random variables this is simple application of the central limit theorem. We present a more elementary proof. This proof requires only Levy's continuity theorem (from which it is standard to prove the central limit theorem), and some basic calculus.

  By Levy's continuity theorem it will suffice to show that the characteristic function to the normalized binomial converges to the that of $\gamma$. In particular, we will show that 
  \[
    \mathrm{E}[e^{is\frac1{\sqrt{N}}W_N}] = \cos^N(\frac1{\sqrt{N}}s) \to e^{-\frac12 s^2}.
  \]
\end{proof}

% Notably, this concept can be used to construct a continuous-time analogue known as a Wiener proccess. We could first consider normalizing the random walk so that it completes $N$ steps over some fixed unit of time. However with the step size $\delta = 1$ we travel a total of $N$ units in that time. We further normalize the step size $\delta = 1/\sqrt{N}$ so that the total distance traveled is precisely $\delta^2N = 1$. 




% We begin with the well known fact that the symmetric binomial distribution given by
% \[
%   f \mapsto \frac{1}{2^N} \sum_{x = 0}^N \binom{N}{x} f(x)
% \]
% converges in some sense to the Gaussian distribution. The symmetric binomial distribution models the number of successes in a series of $N$ repeated independent Bernoulli trials, each defined by
% \[
%   X_t =
%   \begin{cases}
%     0 & \text{with probability } \frac12 \\
%     1 & \text{with probability } \frac12
%   \end{cases}
% \]


Consider flipping a loaded coin with probability $p \in [0,1]$ of landing on heads, and thus probability $(1 - p)$ of landing on tails. The probability of $k$ heads in $N$ coin flips is given by the binomial probability density,
\[
  \binom{N}{k}p^k(1-p)^{N-k}
\]
where $N \in \NN_0$ and $k = 0, 1, \ldots, N$. It is well known that the binomial distribution can be seen as a discrete analog to the Gaussian distribution. Thus we may expect that a discrete analog to the GRT may be defined via the binomial distribution.

In order to draw a clearer line between the binomial and Gaussian densities we make use of an alternate probabilistic model: the Bernoulli random walk. Picture a particle ``walking'' along the integer lattice $\ZZ$, beginning at the origin $x = 0$. At every step, we flip the loaded coin described above, stepping to the right if it lands on heads, and the left if tails. After $N$ flips, the particle's position is 
\[
  x = (\text{\# of heads}) - (\text{\# of tails}) = k - (N - k) = 2k - N
\]
Now the set of possible positions is $x \in [[N]] := \{-N, -N+2, \ldots, N\}$, and the probability of each is precisely the probability of landing $k = \frac{N + x}2$ heads, that is,
\[
  \binom{N}{\frac{N + x}2}p^{\frac{N + x}2}(1 - p)^{N - \frac{N + x}2}
  = \binom{N}{\frac{N + x}2}p^{\frac{N + x}2}(1 - p)^{\frac{N - x}2}
\]
We will define \emph{centered binomial density} supported on $[[N]]$ by
\[
  B_N(x) = \binom{N}{\frac{N+x}2}p^{\frac{N+x}2}(1-p)^{\frac{N-x}2}.
\]
Since the expected displacement at each (independent) step is $p - (1 - p) = 2p - 1$, we calculate the expected position after $N$ steps to be 
\[
  E(B_N) = 2Np-N.
\]
Furthermore the variance of each displacement step is $4p(1-p)$ so that the variance of $B_N$ is
\[
  Var(B_N) = 4Np(1-p)
\]
The earlier claim that the binomial density is a discrete analog to the Gaussian density can be made explicit by the following limit relation. Let \[
  z = \frac{x - E(B_N)}{\sqrt{Var(B_N)}} 
  = \frac{x - 2Np + N}{2\sqrt{Np(1-p)}}
\]
so that $z$ has mean $0$ and variance $1$ with respect to $B_n$. Equivalently we may set
\[
  x = z\sqrt{Var(B_N)} + E(B_N) = 2z\sqrt{Np(1-p)} + 2Np + N
\]
Then we have
\[
  \lim_{N \rightarrow \infty} B_N(x) = \frac{1}{\sqrt{2\pi}}e^{-\frac{z^2}2} = \gamma(z).
\]
This limit is perhaps one of the simplest cases of the robust central limit theorem, but can be proven in a  more elementary ways.

\begin{remark}
  Under an analogous limit a random walk process $x$ is transformed into a Brownian motion process $z$. 
\end{remark}

Having justified the the centered binomial densities $B_N(x)$ as discrete analogs of the Gaussian $w(z)$, we would like to define a sequence of polynomials orthogonal with respect to $B_N(x)$, as the Hermite polynomials are to $w(z)$. For convenience we start with a generating function 

\begin{definition}
  The Krawtchouk polynomials $K_k^{N,p}(x)$ may be defined by the generating function
  \[
    \sum_{k=0}^N K^{N,p}_k(x)y^k = (1 + y)^{\frac{N + x}2}(1 - y)^{\frac{N - x}2}
  \]
\end{definition}
% \begin{remark}
%   Note that this is an ordinary generating function, while that of the Hermite polynomials was a exponential generating function. Is this distinction consequential for us?
% \end{remark}

The polynomials $K^{N,p}_k(x)$ satisfy the orthogonality property
\[
  \sum_{x \in [[N]]} K^{N,p}_k(x) K^{N,p}_\ell(x) B_N(x) = 0, \qquad k \neq \ell
\]
and can be written explicitly as
\[
  K^{N,p}_k(x) = \binom{N}{k} \pFq{2}{1}{-k,(x - N)/2}{-N}{2}
\]

The Krawtchouk and Hermite polynomials are related by the same limiting process.
\begin{proposition}
  With $x = 2 z \sqrt{Np(1-p)} + 2Np + N$ we have the following limit relation:
  \[
    \lim_{N \rightarrow \infty} K^{N,p}_k(x) = H_k(z)
  \]
\end{proposition}

\begin{proof}
  We prove the simpler 
\end{proof}

Now, heuristically we expect a formula analagous to (\ref{eq:GRH}) in the from
\[
  GR_{K^{N,p}_\alpha}(\omega, p) = K^{N,p}_k(p)\omega^\alpha, \qquad |\alpha| = k
\]
where 
\[
  K^{N,p}_\alpha(x) = \prod_{i = 1}^n K^{N,p}_{\alpha_i}(x_i)
\]
We should resolve the conflicting variables both named $p$, perhaps the Krawtchouk $p$ ought to be a $q$ or isn't necessary in the first place.

The desired formula would represent a discrete analog for the Gaussian Radon transform on the finite cubic lattice $[[N]]^n$, however it is not yet clear how to interpret this. An immediate concern is that the cubic lattice does not admit ``hyperplanes'' for arbitrary $p$ and $\omega$. Indeed in the worst case, if $\omega$ is not rational (that is the ratios between coordinates of $\omega$ are not rational, or equivalently the hyperspherical coordinates of $\omega$ include an angle which is an irrational multiple of $\pi$) then a hyperplane orthogonal can contain at most one lattice point. In the case when $\omega$ is rational — in the sense above — we may restrict $p$ to the projection of the lattice onto the span of $\omega$, and sum over the lattice hyperplane $\inner{x, \omega} = p$ with respect to the binomial weight centered on $p\omega$. It remains to be seen whether such an interpretation agrees with the heuristic formula above.

Take the symmetric random walk, where the coin is fair ($p = 1 - p = \frac12$). The position after $N$ flips has distribution
\[
  B_N(x) = \frac1{2^N}\binom{N}{\frac{N+x}2}, \qquad x \in [[N]]
\]
with expected value $E(B_N) = 0$ and variance $Var(B_N) = N$. The limiting process is then given by $B_N(x) \rightarrow w(z)$ where 
\[
  z = \frac{x}{\sqrt{N}}
\]
and further $K^{N,\frac12}_k(x) \rightarrow H_k(z)$.

Now consider the following scenario in two dimensions. A particle starting at the origin $x = (x_1, x_2) = 0$ flips two fair coins, stepping down/up depending on the first coin, left/right depending on the second. This means the particle moves one unit up and right, up and left, down and right, or down and left, with equal probability. 

\section{The proposed discrete GRT}

% \section{A limit for powers of cosine}

% Here we will prove the following limit:
% \[
  
% \]